Argennon: A Scalable Smart Contract Platform

### 2021-06-22 tex/sections/consensus.tex
Fix some typos
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

The delegates committee generates a certificate for every block of the Argennon blockchain, and the
validators committee generates a certificate every $m$ blocks. The validators committee will
certify a block only if it has already been certified by the committee of delegates.

In addition to primary committees, Argennon has several community driven committees. Certificates of these
committees are not required for block validation, but they could be used by the members of the validators
committee to better decide about the validity of a block.

When an anomaly is detected in the consensus mechanism, the \emph{recovery} protocol is initiated by nodes. The
recovery protocol is designed to be resilient to many types of attacks in order to be able to restore the normal
system functionality.

@@

Usually, the delegates are large organizations, and they have enough computational resources to generate blocks
very fast. However, a block is not completely final if it does not have the certificate of the validators committee.
A certified block by the delegates will not be accepted by the network, if the last block certified by
the validators committee is behind more than a certain number of blocks.

@@

A block certificate issued by some members of the validators committee is considered valid, if according to
the staking database of the previous \textbf{certified block by the validators committee}, we have:
\begin{itemize}
    \item The total stake of \texttt{online} accounts is higher than \texttt{minOnlineStake} percent of the
    total stake of all accounts. This threshold can be changed by the ADAGs, but it can never be lower
    than 70 percent.
    \item All signers of the certificate have \texttt{online} status.
    \item The sum of stake values of the certificate signers is higher than 80 percent of the total stake
    of accounts that have \texttt{online} status.
\end{itemize}

@@

More precisely, to decide about signing the block certificate, a honest member of the validators
committee iterates over every block of the validation set, and selects a block for validation with
probability $p_u$. In this way, a member of the validators committee will select $p_{u}m$ blocks in expectation.
Then, the honest member conditionally validates the selected blocks. If the member has selected more than one block,
he may validate the selected blocks in parallel.
If all checked blocks are valid, the validator issues an "accept"
signature, otherwise he issues a "reject" signature.

One recommended formula for calculating the probability of selecting a block for validation by user $u$ is:
\begin{equation}
    p_u=\max\left(\frac{s_u}{m\mu},\ \frac{1}{m}\right),\label{eq:block-selection}
\end{equation}
where $\mu$ is the average stake of committee members and $s_u$ is the stake of user $u$.

The value of $m$ is determined by the ADAGs. but it can never be set higher than $100$. This way, it is guaranteed
that on average, any block of the Argennon blockchain is validated by at least $0.005$ of the total ARG supply.

@@

Any member of a group knows all the servers that are responsible for signature aggregation of his group. When a member
signs a block certificate, he sends his signature to \textbf{all} the severs that aggregate the signatures of his group.
These servers aggregate the signatures they receive, and then send the aggregated signature to the delegates.
Furthermore, the delegates aggregate these signatures to produce the final block certificate,
and then include it in the next block.

@@

To mitigate this problem, Argennon uses a hybrid approach for estimating the stake of a user.
Every \texttt{stakingDuration} blocks, which is called a \emph{staking period}, Argennon calculates
a \emph{trust value} for each user. The user's stake
at time step \(t\), is estimated based on the user's trust value and his ARG balance:
\[
    S_{u,t} = \min (B_{u,t}, Trust_{u,k}),
\]
where:
\begin{itemize}
    \item \(S_{u,t}\) is the stake of user \(u\) at time step \(t\).
    \item \(B_{u,t}\) is the ARG balance of user \(u\) at time step \(t\).
    \item \(Trust_{u,k}\) is an estimated trust value for user \(u\) at staking period \(k\).
\end{itemize}

Argennon users can lock their ARG tokens in their account for any period of time. During this time a user
will not be able to transfer his tokens and there is no way for cancelling a lock.
The trust value of a user is calculated based on the amount of his locked tokens and the
Exponential Moving Average (EMA) of his ARG balance:
\[
    Trust_{u,k} = L_{u,k} + M_{u,t_k}\ ,
\]
where
\begin{itemize}
    \item $L_{u,k}$ is the amount of locked tokens of user $u$, whose release time is \textbf{after the end} of
    the staking period $k+1$.
    \item $M_{u,t_k}$ is the Exponential Moving Average (EMA) of the ARG balance of user \(u\) at time step \(t_k\).
    $t_k$ is the start time of the staking period $k$.
\end{itemize}

@@

For calculating the EMA of a user's balance at time step \(t\), we can use the following
recursive formula:
\[
    M_{u,t} = (1 - \alpha) M_{u,t-1} + \alpha B_{u,t} = M_{u,t-1} + \alpha (B_{u,t} - M_{u,t-1})
\]
where the coefficient \(\alpha\) is a constant smoothing factor between \(0\) and \(1\), which represents the
degree of weighting decrease. A higher \(\alpha\) discounts older observations faster.

Usually an account balance will not change in every time step, and we can use older values of EMA for calculating
\(M_{u,t}\): (In the following equations the \(u\) subscript is dropped for simplicity)
\[
    M_{t} = (1 - \alpha)^{t-k}M_{k} + [1 - (1 - \alpha)^{t - k}]B
\]
where:
\[
    B = B_{k+1} = B_{k+2} = \dots = B_{t}
\]
We know that when \(|nx| \ll 1\) we can use the binomial approximation \({(1 + x)^n \approx 1 + nx}\). So, we can
further simplify this formula:
\[
    M_{t} = M_{k} + (t - k) \alpha (B - M_{k})
\]

For choosing the value of \(\alpha\) we can consider the number of time steps that the trust value of a user needs
for reaching a specified fraction of his account balance. We know that for large \(n\) and \(|x| < 1\) we have
\((1 + x)^n \approx e^{nx}\), so by letting \(M_{u,k} = 0\) and \(n = t - k\) we can write:
\[
    \alpha =- \frac{\ln\left(1 - \frac{M_{n+k}}{B}\right)}{n}
\]
The value of \(\alpha\) for a desired configuration can be calculated by this equation. For instance, we could
calculate the \(\alpha\) for a relatively good configuration in which \(M_{n+k} = 0.8B\) and \(n\) equals to the
number of time steps of 10 years.

>>>>

The committee of delegates generates a certificate for every block of the Argennon blockchain, and the
committee of validators generates a certificate every $m$ blocks. The validators' committee will
certify a block only if it has already been certified by the committee of delegates.

In addition to primary committees, Argennon has several community driven committees. Certificates of these
committees are not required for block finality, but they could be used by the members of the
validators' committee to better decide about the validity of a block.

When an anomaly is detected in the consensus mechanism, the \emph{recovery} protocol is initiated by nodes. The
recovery protocol is designed to be resilient to many types of attacks in order to be able to restore the normal
functionality of the system.

@@

Usually, the delegates are large organizations, and they have enough computational resources to generate blocks
very fast. However, a block is not completely final if it does not have the certificate of the validators' committee.
A certified block by the delegates will not be accepted by the network, if the last block certified by
the validators is behind it more than a certain number of blocks.

@@

A block certificate issued by some members of the validators committee is considered valid, if according to
the staking database of the previous \textbf{certified block by the validators' committee}, we have:
\begin{itemize}
    \item The total stake of \texttt{online} accounts is higher than \texttt{minOnlineStake} percent of the
    total stake of all accounts. This threshold can be changed by the ADAGs, but it can never be lower
    than 70 percent.
    \item All signers of the certificate have \texttt{online} status.
    \item The sum of stake values of the certificate signers is higher than 80 percent of the total stake
    of accounts that have \texttt{online} status.
\end{itemize}

@@

More precisely, to decide about signing the block certificate, a honest member of the validators'
committee iterates over every block of the validation set, and selects a block for validation with
probability $p_u$. In this way, a member of the validators' committee will select $p_{u}m$ blocks in expectation.
Then, the honest member conditionally validates the selected blocks. If the member has selected more than one block,
he may validate the selected blocks in parallel.
If all checked blocks are valid, the validator issues an "accept"
signature, otherwise he issues a "reject" signature.

One recommended formula for calculating the probability of selecting a block by user $u$ for validation is:
\begin{equation}
    p_u=\max\left(\frac{s_u}{m\mu},\ \frac{1}{m}\right),\label{eq:block-selection}
\end{equation}
where $\mu$ is the average stake of committee members and $s_u$ is the stake of user $u$.

The value of $m$ is determined by the ADAGs. but it can never be higher than $100$. This way, it is guaranteed
that on average, any block of the Argennon blockchain is validated by at least $0.005$ of the total ARG supply.

@@

Any member of a group knows all the servers that are responsible for signature aggregation of his group. When a member
signs a block certificate, he sends his signature to \textbf{all} the severs that aggregate the signatures of his group.
These servers aggregate the signatures they receive and then send the aggregated signature to the delegates.
Furthermore, the delegates aggregate these signatures to produce the final block certificate
and then include it in the next block.

@@

To mitigate this problem, Argennon uses a hybrid approach for estimating the stake of a user.
Every \texttt{stakingDuration} blocks, which is called a \emph{staking period}, Argennon calculates
a \emph{trust value} for each user. The user's stake
at time step \(t\), is estimated based on the user's trust value and his ARG balance:
\begin{equation}
    S_{u,t} = \min (B_{u,t}, Trust_{u,k})\ ,\label{eq:stake}
\end{equation}
where:
\begin{itemize}
    \item \(S_{u,t}\) is the stake of user \(u\) at time step \(t\).
    \item \(B_{u,t}\) is the ARG balance of user \(u\) at time step \(t\).
    \item \(Trust_{u,k}\) is an estimated trust value for user \(u\) at staking period \(k\).
\end{itemize}

Argennon users can lock their ARG tokens in their account for any period of time. During this time a user
will not be able to transfer his tokens and there is no way for cancelling a lock.
The trust value of a user is calculated based on the amount of his locked tokens and the
Exponential Moving Average (EMA) of his ARG balance:
\begin{equation}
    Trust_{u,k} = L_{u,k} + M_{u,t_k}\ ,\label{eq:trust}
\end{equation}
where
\begin{itemize}
    \item $L_{u,k}$ is the amount of locked tokens of user $u$, whose release time is \textbf{after the end} of
    the staking period $k+1$.
    \item $M_{u,t_k}$ is the Exponential Moving Average (EMA) of the ARG balance of user \(u\) at time step \(t_k\).
    $t_k$ is the start time of the staking period $k$.
\end{itemize}

@@

For calculating the EMA of a user's balance at time step \(t\), we can use the following
recursive formula:
\[
    M_{u,t} = (1 - \alpha) M_{u,t-1} + \alpha B_{u,t} = M_{u,t-1} + \alpha (B_{u,t} - M_{u,t-1})\ ,
\]
where the coefficient \(\alpha\) is a constant smoothing factor between \(0\) and \(1\), which represents the
degree of weighting decrease. A higher \(\alpha\) discounts older observations faster.

Usually an account balance will not change in every time step, and we can use older values of EMA for calculating
\(M_{u,t}\): (In the following equations the \(u\) subscript is dropped for simplicity)
\[
    M_{t} = (1 - \alpha)^{t-k}M_{k} + [1 - (1 - \alpha)^{t - k}]B\ ,
\]
where:
\[
    B = B_{k+1} = B_{k+2} = \dots = B_{t}\ .
\]
We know that when \(|nx| \ll 1\) we can use the binomial approximation \({(1 + x)^n \approx 1 + nx}\). So, we can
further simplify this formula:
\[
    M_{t} = M_{k} + (t - k) \alpha (B - M_{k})\ .
\]

For choosing the value of \(\alpha\) we can consider the number of time steps that the trust value of a user needs
for reaching a specified fraction of his account balance. We know that for large \(n\) and \(|x| < 1\) we have
\((1 + x)^n \approx e^{nx}\), so by letting \(M_{u,k} = 0\) and \(n = t - k\) we can write:
\begin{equation}
    \alpha =- \frac{\ln\left(1 - \frac{M_{n+k}}{B}\right)}{n}\ .\label{eq:alpha}
\end{equation}
The value of \(\alpha\) for a desired configuration can be calculated by this equation. For instance, we could
calculate the \(\alpha\) for a relatively good configuration in which \(M_{n+k} = 0.8B\) and \(n\) equals to the
number of time steps of 10 years.

### 2021-06-22 tex/sections/elements.tex
Fix some typos
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

Argennon accounts are entities defined inside the ARG smart contract.
Every Argennon account is uniquely identified by a prefix code generated using \emph{accounts} prefix tree. An account
identifier can be considered as the address of an account and has the following standard symbolic representation:
\begin{verbatim}
<account-id> ::= "["<decimal-prefix-code>"]"
<decimal-prefix-code> ::= <dec-num>"."<decimal-prefix-code> | <dec-num>
\end{verbatim}
where \texttt{<dec-num>} is a normal decimal number between $0$ and $255$.

@@

To be able to detect invalid signatures, we keep the maximum nonce of used digital signatures per user. When the
difference between \texttt{issuance} component of this nonce and the current round becomes bigger than the
maximum allowed lifetime of a signature, this information can be safely deleted.\footnote{in some conventional
blockchains, the nonce data can never be deleted, even if the account has zero balance and is not used anymore.}

>>>>

Argennon accounts are entities defined inside the ARG smart contract.
Every Argennon account is uniquely identified by a prefix code generated using \emph{accounts} prefix
tree. (See Section~\ref{sec:identifiers}) An account
identifier can be considered as the address of an account and has the following standard symbolic representation:
\begin{verbatim}
<account-id> ::= "["<decimal-prefix-code>"]"
<decimal-prefix-code> ::= <dec-num>"."<decimal-prefix-code> | <dec-num>
\end{verbatim}
where \texttt{<dec-num>} is a normal decimal number between $0$ and $255$.

@@

To be able to detect invalid signatures, we keep the maximum nonce of used digital signatures per user. This information
is stored in the ARG smart contract and when the difference between \texttt{issuance} component of the nonce and
the current round becomes bigger than the maximum allowed lifetime of a signature, it can be safely
deleted.\footnote{in some conventional
blockchains, the nonce data can never be deleted, even if the account has zero balance and is no longer used.}

### 2021-06-22 tex/sections/persistence.tex
Fix some typos
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

In the AVM persistence layer, similar objects are clustered together and constitute a bigger data element which we call
a \emph{page}.\footnote{we avoided calling them clusters, because usually a cluster refers to a \emph{set}. AVM object
clusters are not sets. They are ordered lists, like a page containing an ordered list of words or sentences.}
A page is an ordered list of an arbitrary number of objects, which their order reflects the order they were added to
the page:
\[
    P = (O_1,O_2,\dots,O_n),\quad i < j \; \Leftrightarrow \; \textrm{$O_i$ was added before $O_j$}
\]

@@

We consider the following properties for a ZK-EDB:
\begin{itemize}
    \item The ZK-EDB contains a mapping from a set of keys to a set of values.
    \item Every state of the database has a commitment \(C\).
    \item The ZK-EDB has a method \((D, \pi) = \text{get}(x)\), where \(x\) is a key and \(D\) is the associated data
    with \(x\), and \(\pi\) is a proof.
    \item A user can use \(C\) and \(\pi\) to verify that \(D\) is really associated with \(x\), and \(D\) is not
    altered. Consequently, a user who can obtain \(C\) from a trusted source does not need to trust the ZK-EDB\@.
    \item Having \(\pi\) and \(C\) a user can compute the commitment \(C'\) for the database in which \(D'\) is
    associated with \(x\) instead of \(D\).
\end{itemize}

@@

The commitments of the AVM ZK-EDBs are affected by the way the clustering of data objects is done. So,
the clustering algorithm has to be a part of the Argennon consensus protocol.

@@

A block proposer could obtain clustering directives from any third party source\footnote{we can say the AVM clustering
algorithm is essentially off-chain.}. This will not
affect Argennon security, since the integrity of a database can not be altered by clustering directives.
Those directives can only affect the performance of the argennon blockchain, and directives of a single block can
not affect the performance considerably.

>>>>

In the AVM persistence layer, similar objects are clustered together and constitute a bigger data element which we call
a \emph{page}.\footnote{we avoid calling them clusters, because usually a cluster refers to a \emph{set}. AVM object
clusters are not sets. They are ordered lists, like a page containing an ordered list of words or sentences.}
A page is an ordered list of an arbitrary number of objects, which their order reflects the order they were added to
the page:
\[
    P = (O_1,O_2,\dots,O_n),\quad i < j \; \Leftrightarrow \; \textrm{$O_i$ was added before $O_j$}\ .
\]

@@

We consider the following properties for a ZK-EDB:
\begin{itemize}
    \item The ZK-EDB contains a mapping from a set of keys to a set of values.
    \item Every state of the database has a commitment \(C\).
    \item The ZK-EDB has a method \((D, \pi) = \text{get}(x)\), where \(x\) is a key and \(D\) is the associated data
    with \(x\), and \(\pi\) is a proof.
    \item A user having \(C\) and \(\pi\) can verify that \(D\) is really associated with \(x\), and \(D\) is not
    altered. Consequently, a user who can obtain \(C\) from a trusted source does not need to trust the ZK-EDB\@.
    \item Having \(\pi\) and \(C\) a user can compute the commitment \(C'\) for the database in which \(D'\) is
    associated with \(x\) instead of \(D\).
\end{itemize}

@@

The commitments of the AVM ZK-EDBs are affected by the way data objects are clustered. Therefore,
the Argennon clustering algorithm has to be a part of the consensus protocol.

@@

A block proposer could obtain clustering directives from any third party source\footnote{we can say the AVM clustering
algorithm is essentially off-chain.}. This will not
affect Argennon security, since the integrity of a database can not be altered by clustering directives.
Those directives can only affect the performance of the Argennon network, and directives of a single block can
not affect the performance considerably.
